%----------------------------------------------------------------------------------------
%
% COMSC-4173: Mobile Applications - Section 1423
%
% Project Report 1
%
% Created by Thomas W. Crews on Monday, January 9, 2017
%
%
% !!! MUST COMPILE WITH XeLaTeX ENGINE !!!
%
%----------------------------------------------------------------------------------------
%
\documentclass[letterpaper]{article}            % Defines type of document and paper size
%
%----------------------------------------------------------------------------------------
% MODULE IMPORTS
%
\usepackage[english]{babel}                     % Not entirely sure, maybe spellcheck?
\usepackage[utf8]{inputenc}                     % Encoding information (don't touch)
\usepackage[margin=1.0in]{geometry}             % This module honestly scares me
\usepackage{fontspec}                           % Allows advanced font formatting
\usepackage{hyperref}                          % Allows linking between sections
%\usepackage{soul}                              % Basically just for strikeout text
%\usepackage{minted}                            % Syntax highlighting - requires PYGMENTS
%\usepackage{array}                             % Allows advanced table formatting
%\usepackage[table]{xcolor}                     % Allows table shading
%
%----------------------------------------------------------------------------------------
% FONT SETTINGS
%
\setmainfont[Scale=1.1]{Helvetica Neue}         % Define main font and its scale
\setmonofont[Scale=1.1]{Courier New}            % Define monospaced font likewise
%
% Note that Helvetica Neue is only available by default on Apple's Mac OS X 10.6 or newer
% and that Inconsolata is likely not installed by default on any major operating systems.
%
%----------------------------------------------------------------------------------------
% PRINTED DOCUMENT INFORMATION
%
\title{Mobile Applications}                     % Set title
\author{Project Report 1}                       % Set author (subtitle, in this case)
\date{Created by Tommy Crews on \today}         % Date of typesetting
%
%----------------------------------------------------------------------------------------

\begin{document}

\newcommand{\code}[1]{\texttt{#1}}              % I use this for inline code and such

\setcounter{section}{1}							% Use when beginning with subsection

\maketitle                                      % Just prints the title


%\tableofcontents                               % For bigger documents, prints ToC

%----------------------------------------------------------------------------------------
%
% PREDEFINED STRINGS
%
%----------------------------------------------------------------------------------------
%	MAIN
%----------------------------------------------------------------------------------------

% I'll be using these big comment headers to keep track of sections. Subsections are
% delineated by single lines of dashes. Sub-subsections are on their own.

%\section{}

%----------------------------------------------------------------------------------------

\subsection{What is Your Question?}

\subsubsection{What question are you interested in?}

Can a mobile device be used for quick and effective network testing and diagnosis?

\subsubsection{What skills that you develop in answering this question are you excited about?}

I am excited about improving my limited skills in computer networking.

\subsubsection{What are the things about this question that are interesting to you?}

Very few tools exist for developers and I.T. specialists. A mobile multi-tool for observing network activity could prove incredibly handy for fast diagnosis and improving uptime. This application would have unlimited potential. Apart from observing network information, the application could offer a likely prognosis for network errors, and could then even attempt to automatically address the issue.

\subsubsection{What are a few other possible questions you have considered?}

"Can augmented reality be used to locate lost items?"

"Does the world have space for another successful mobile game?"

"Can peer-to-peer sharing be developed into a mobile application?"

\subsubsection{What is wrong with the other questions that makes them less desirable?}

Augmented reality requires very heavy and inefficient API use. It is still an extremely new technology that doesn't work well on single-camera devices like mobile phones.

The App Store and Google Play store are arguably saturated with games, with an estimated 0.05\% of all submitted games actually considered successful. A game is fun but not useful over time. Utilities are more my style.

Most smartphones have sandboxing implementations that would make sharing without an intermediate hosting service impossible. Too many other sharing services already exist, and the majority of such operations are now handled by cloud services.

\subsubsection{How will answering this question help you have a better understanding of this class?}

Developing such an application will expose me to many new API methods and networking protocols. Research will be required.

\subsubsection{Is this question useful to anyone outside this class?}

Any network administrators and perhaps organization executives would find such an application incredibly useful.

\subsubsection{How does this question benefit your career progression?}

Increasing my networking knowledge and skill will give me a more broad skill set in the realm of computer science.

\subsubsection{What employers are also interested in this type of question?}

Any institution offering network services, as well as any institution that makes use of any networking technology (literally everyone) will find this application useful.

\subsubsection{What other classes can you also explore this question in?}

Computer Science Capstone or Computer Forensics, as well as Data Communications and Networking.
%----------------------------------------------------------------------------------------

\subsection{What did you get done this week for your project?}

\subsubsection{What did you get done?}

Brainstorming of project function and design ideas. Development of project codename and provisioning profiles. Establishment of Git repository and connection of repository to GitHub.

\subsubsection{What documentation did you find and what code did you write?}

Information for iOS app designs was found at the following addresses:

\url{https://developer.apple.com/design/}

\url{https://developer.apple.com/ios/human-interface-guidelines/overview/}

\url{https://developer.apple.com/watchos/human-interface-guidelines/overview/}

\url{https://developer.apple.com/app-store/marketing/guidelines/}

\subsubsection{How much time did you spend working on your project?}

I spent around ten hours this week on this project.

\subsubsection{What new ideas, questions, and concerns have you had?}

A list of services to be offered by the application must be developed.

%----------------------------------------------------------------------------------------

\subsection{What do you plan to accomplish next week?}

\subsubsection{What is your deliverable goal for the next week?}

Create the first prototype of the project.

\subsubsection{What tasks will you complete next week to meet that goal?}

Basic UI design, initial marketing design, and compilable simulation.

\subsubsection{How much time will you have next week to work on your project?}

10-16 hours.

%----------------------------------------------------------------------------------------

\subsection{What is keeping you from being successful?}

\subsubsection{What is it that is keeping you from being successful in your project?}

This week my biggest hindrance was deciding on a project.

\subsubsection{Is this the same problem you have had in other classes?}

Not really; my other classes are far more directly instructional, and not self-planned.

\subsubsection{What are you doing to get this fixed?}

The issue has been resolved. I realized by creating an application to benefit me and not just others, I would be far more motivated to invest time into it.

\subsubsection{What have you asked others to do in order to fix this problem?}

I asked friends and family for help in brainstorming application ideas.

\end{document}

% SDG
