%----------------------------------------------------------------------------------------
%
% COMSC-4173: Mobile Applications - Section 1423
%
% Project Report 5
%
% Created by Thomas W. Crews on Wednesday, February 8, 2017
%
%
% !!! MUST COMPILE WITH XeLaTeX ENGINE !!!
%
%----------------------------------------------------------------------------------------
%
\documentclass[letterpaper]{article}            % Defines type of document and paper size
%
%----------------------------------------------------------------------------------------
% MODULE IMPORTS
%
\usepackage[english]{babel}                     % Not entirely sure, maybe spellcheck?
\usepackage[utf8]{inputenc}                     % Encoding information (don't touch)
\usepackage[margin=1.0in]{geometry}             % This module honestly scares me
\usepackage{fontspec}                           % Allows advanced font formatting
\usepackage{hyperref}                           % Allows linking between sections
%\usepackage{soul}                              % Basically just for strikeout text
%\usepackage{minted}                            % Syntax highlighting - requires PYGMENTS
%\usepackage{array}                             % Allows advanced table formatting
%\usepackage[table]{xcolor}                     % Allows table shading
%
%----------------------------------------------------------------------------------------
% FONT SETTINGS
%
\setmainfont[Scale=1.1]{Helvetica Neue}         % Define main font and its scale
\setmonofont[Scale=1.1]{Courier New}            % Define monospaced font likewise
%
% Note that Helvetica Neue is only available by default on Apple's Mac OS X 10.6 or newer
% and that Inconsolata is likely not installed by default on any major operating systems.
%
%----------------------------------------------------------------------------------------
% PRINTED DOCUMENT INFORMATION
%
\title{Mobile Applications}                     % Set title
\author{Project Report 5}                       % Set author (subtitle, in this case)
\date{Compiled in Xe\LaTeX{} by Tommy Crews on \today}         % Date of typesetting
%
%----------------------------------------------------------------------------------------

\begin{document}

\newcommand{\code}[1]{\texttt{#1}}              % I use this for inline code and such

\setcounter{section}{5}							% Use when beginning with subsection

\maketitle                                      % Just prints the title


%\tableofcontents                               % For bigger documents, prints ToC

%----------------------------------------------------------------------------------------
%
% PREDEFINED STRINGS
%
%----------------------------------------------------------------------------------------
%	MAIN
%----------------------------------------------------------------------------------------

% I'll be using these big comment headers to keep track of sections. Subsections are
% delineated by single lines of dashes. Sub-subsections are on their own.

%\section{}

%----------------------------------------------------------------------------------------

\subsection{Please paraphrase or restate your question.}

\subsubsection{Please paraphrase or restate your question from Chapter 1. Now is not the time to be making significant changes to your question. Take advantage of your current time to get something delivered for your project.}

Can this be more than a network analysis application?

%----------------------------------------------------------------------------------------

\subsection{Where do you see yourself in five years?}

This is an interview question. I want you to think about this as it pertains to your project. Who are some people in your field that are five to fifteen years ahead of you? Who are some people that are a year ahead of you? How can you do what they have done? How can you help yourself be prepared for future opportunities?

\subsubsection{Who would be a good outside judge for your solution?}

I would like to allow SWOSU's own I.T. professionals to judge my solution, as well as my grandparents, who themselves are completely technologically illiterate.

\subsubsection{What would you like outside feedback on?}

General usability of the application, as well as its effectiveness in a professional field.

\subsubsection{What would you like your outside assessor to ignore?}

At this time, I would like them to ignore the lack of more advanced networking features. Such things have yet to be implemented on mobile devices, and will take some research on my part.

\subsubsection{Who are global experts in the field you are working in?}

Cloud and network infrastructure professionals, like our own Neal Xiong.

\subsubsection{What paths did they take to become global experts?}

Pioneering work in their field. Creating scientific journal articles. Making new steps in networking.

\subsubsection{What would you like to do differently from them?}

I would like to take their pioneering and port it to a simple and usable form for all users.

\subsubsection{What would you like to do the same?}

I would like to find new ways of doing things, and change the way they're done.

\subsubsection{What can you do to be more prepared for future opportunities in your life?}

I hope to plan more for the future in terms of academic degrees and career paths. I'm still unsure of what field I would like to pursue.

%----------------------------------------------------------------------------------------

\subsection{What did you get done this week for your project?}

\subsubsection{What did you get done?}

This week, I laid the foundation for IPv4 checking, and began research into bandwidth and latency tests. I also streamlined the error-checking process developed last week.

\subsubsection{How much time did you spend working on your project?}

This week, I spent around 14 hours working on the project.

%----------------------------------------------------------------------------------------

\subsection{What do you plan to accomplish next week?}

\subsubsection{What is your overall deliverable goal for the next week?}

I plan to resolve any existing issues and push forward adding network features.

\subsubsection{What are the tasks you will complete to reach this goal?}

Swift research will be conducted concerning network capabilities, as well as limitations imposed by iOS. A new view controller will be added for diagnostic purposes.

\subsubsection{How much time will you have next week to work on your project?}

10-16 hours.

%----------------------------------------------------------------------------------------

\subsection{What is keeping you from being successful?}

\subsubsection{What has kept you from producing so far in the semester?}

At this time, the project is moving forward smoothly. I was late to submit this report.

\subsubsection{What could someone else do to fix this problem for you?}

After my experience in Software Engineering, I believe I work best alone on these types of projects. If anything, I would like to have a test dummy.

\subsubsection{What is it that is keeping you from being successful in your goals for next week?}

Nothing at this time is obstructing this project's development.

\subsubsection{How do you feel about your project and giving up on it to help someone else?}

I am fairly excited about my project. I am open to helping others, but I want to see my project through to the end.

\subsubsection{How do you feel about asking someone else to help you on your project?}

I don't believe any other students are familiar enough with this highly unique language and IDE to help with my project.

\end{document}

% SDG
